Intended Table of Contents Thesis

### 2013-02-07 Chapters/Chapter2.tex
Added intended thesis outline

% Chapter 2

@@

The following steps are performed, which are explained below and illustrated 
in figure *** [add figure with plot of sets] \ref{}:
\begin{enumerate}
	\item \textbf{Gather data} and represent them in a chosen number of 
	features,
	\item \textbf{Subtract mean} to center the data around the axis. The new 
	data set will have mean zero,
	\item \textbf{Generate covariance matrix} by calculating all pairwise 
	feature variances,
	\item \textbf{Calculate Eigenvectors and Eigenvalues} of the covariance 
	matrix. The Eigenvectors are then normalized to make further calculations 
	easier,
	\item \textbf{Generate feature vector} which indicated which features are 
	characteristic or meant to keep in de data set, by comparing the 
	Eigenvalues. 
\end{enumerate}

@@

\subsection{$k$-means clustering}
[EXPLAIN] divide data set $n$ into $k$ clusters.

>>>>

% Chapter 2
% !TEX root = ../main.tex

@@

The following steps are performed, which are explained below and illustrated
in figure *** [add figure with plot of sets]:

\begin{enumerate}
	\item \textbf{Gather data} and represent them in a chosen number of
	features,
	\item \textbf{Subtract mean} to center the data around the axis. The new
	data set will have mean zero,
	\item \textbf{Generate covariance matrix} by calculating all pairwise
	feature variances,
	\item \textbf{Calculate Eigenvectors and Eigenvalues} of the covariance
	matrix. The Eigenvectors are then normalized to make further calculations
	easier,
	\item \textbf{Generate feature vector} which indicated which features are
	characteristic or meant to keep in de data set, by comparing the
	Eigenvalues.
\end{enumerate}

@@

\subsection{k-means clustering}
[EXPLAIN] divide data set $n$ into $k$ clusters.
